% repository_map.tex --- Repository structure and file roles (trade-reconciliation)
%
% To keep this in sync when you add or move files:
%   1. Update \RepositorySyncDate below.
%   2. Adjust the tree and tables to match the workspace.
%   3. Recompile (e.g. pdflatex repository_map.tex).
%
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

\newcommand{\RepositorySyncDate}{2026-05-14}

\title{Project23---ViseFellowship\\Repository map}
\author{Generated reference (maintain manually or via script)}
\date{Synced: \RepositorySyncDate}

\begin{document}
\maketitle

\begin{abstract}
\sloppy
This document summarizes the layout of the repository root project
\texttt{Project23---ViseFellowship}, with emphasis on the
\texttt{trade-reconciliation/} tree: parsers, reconciliation logic,
optional Rust acceleration, tests, sample data, and generated outputs.
\end{abstract}

\section{Repository root}

The repository root contains a short pointer \path{README.md} and convenience copies of CSV inputs at the top level (\path{trades.csv}, \path{lots.csv}). All runnable code and canonical data for the exercise live under \path{trade-reconciliation/}.

\section[Directory tree (trade-reconciliation)]{Directory tree (\texttt{trade-reconciliation/})}

\begin{verbatim}
trade-reconciliation/
  README.md
  requirements.txt
  .gitignore
  data/
    raw/
      trades.csv
      lots.csv
      (FIDELITY-20250729.txt when present)
    processed/
  docs/
    solution_journal.md
    repository_map.tex   <-- this file
  outputs/
    reconciliation_report.csv      (after run)
    reconciliation_summary.json   (after run)
    sample_console_output.txt      (after run)
  rust-core/
    Cargo.toml
    src/main.rs
  src/
    __init__.py
    main.py
    rust_bridge.py
    parser.py
    models.py
    reconcile.py
    aggregation.py
    utils.py
  tests/
    __init__.py
    test_parser.py
    test_reconcile.py
    test_aggregation.py
\end{verbatim}

\section{Specific folders}

\begin{description}
  \item[\path{trade-reconciliation/src/}] Python package: entry point, parsing, domain models, reconciliation and summaries, CSV/JSON writers, and subprocess bridge to the Rust core.
  \item[\path{trade-reconciliation/tests/}] \texttt{pytest} suite for parser, reconcile, and aggregation behavior.
  \item[\path{trade-reconciliation/data/raw/}] Input artifacts: Vise \path{trades.csv}, \path{lots.csv}, and (when supplied) fixed-width Fidelity \path{FIDELITY-20250729.txt}.
  \item[\path{trade-reconciliation/data/processed/}] Reserved for derived or intermediate data (may be empty).
  \item[\path{trade-reconciliation/rust-core/}] Optional Cargo project: faster parse/reconcile path invoked from Python when \texttt{cargo} is available.
  \item[\path{trade-reconciliation/outputs/}] Written on each successful run: discrepancy report, JSON summary, and captured console text.
  \item[\path{trade-reconciliation/docs/}] Narrative notes (\path{solution_journal.md}) and this repository map.
\end{description}

\section[Specific files under src]{Specific files under \texttt{src/}}

\begin{longtable}{@{}p{0.28\linewidth}p{0.66\linewidth}@{}}
  \caption{Python modules in \texttt{src/} (paths relative to \texttt{trade-reconciliation/}).} \\
  \toprule
  \textbf{File} & \textbf{Role} \\
  \midrule
  \endfirsthead
  \multicolumn{2}{c}{\tablename\ \thetable{} --- \textit{continued}} \\
  \toprule
  \textbf{File} & \textbf{Role} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{2}{r}{\textit{Continued on next page}} \\
  \endfoot
  \bottomrule
  \endlastfoot

  \path{main.py}
  & Orchestrates the pipeline: tries Rust via \path{rust_bridge.py}; parses Vise lots/trades in Python; validates sells vs.\ lots; writes \path{outputs/} CSV/JSON and console capture. \\

  \path{rust_bridge.py}
  & If \texttt{cargo} and \path{rust-core/Cargo.toml} exist, runs \texttt{cargo run --release} with Fidelity and trades paths and reads JSON from a temp file; returns \texttt{None} on failure so Python path runs. \\

  \path{parser.py}
  & Fixed-width Fidelity line parsing (record type \texttt{D}, trade flag, symbol/side/quantity/notional slices) and CSV parsers for Vise trades and lots into \path{models.py} types. \\

  \path{models.py}
  & Frozen dataclasses: \texttt{NormalizedTrade}, \texttt{LotRecord}, \texttt{Discrepancy}; serialization helpers for CSV/JSON-friendly dicts. \\

  \path{reconcile.py}
  & Aggregates trades by \texttt{(symbol, side)}; emits discrepancy rows (missing/extra Fidelity, quantity vs.\ notional mismatch); \texttt{validate\_sell\_quantities\_against\_lots}. \\

  \path{aggregation.py}
  & Builds discrepancy count rollups and notional summaries (by side and by ticker) for the JSON summary when using the Python engine. \\

  \path{utils.py}
  & Implied-decimal parsing, money quantization, \texttt{write\_csv} / \texttt{write\_json}. \\

  \path{__init__.py}
  & Package marker. \\
\end{longtable}

\section{Rust core}

\begin{description}
  \item[\path{rust-core/Cargo.toml}] Crate manifest for the optional native path.
  \item[\path{rust-core/src/main.rs}] CLI: reads Fidelity and Vise trade paths, writes reconciliation JSON for the Python bridge to consume.
\end{description}

\section{Tests}

\begin{tabular}{@{}ll@{}}
  \toprule
  \textbf{File} & \textbf{Focus} \\
  \midrule
  \path{tests/test_parser.py} & Fidelity/Vise parsing correctness \\
  \path{tests/test_reconcile.py} & Aggregation and discrepancy classification \\
  \path{tests/test_aggregation.py} & Summary and count helpers \\
  \bottomrule
\end{tabular}

\section{Configuration and docs}

\begin{description}
  \item[\path{requirements.txt}] Python dependencies for the project.
  \item[\path{.gitignore}] Ignores virtualenv, caches, and generated artifacts as configured.
  \item[\path{README.md}] Setup, run (\texttt{python -m src.main}), test (\texttt{pytest}), and layout overview.
  \item[\path{docs/solution_journal.md}] Working notes and rationale for the assessment.
\end{description}

\section{Outputs (generated)}

After \texttt{python -m src.main} from \path{trade-reconciliation/}:

\begin{description}
  \item[\path{outputs/reconciliation_report.csv}] Row-level discrepancies.
  \item[\path{outputs/reconciliation_summary.json}] Counts, notional summaries, engine (\texttt{rust} vs.\ \texttt{python}), lot warnings, timestamp.
  \item[\path{outputs/sample_console_output.txt}] Captured stdout from the last run.
\end{description}

\end{document}
